Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/evaluation.tex
debug

From Table~\ref{table:base_benchmark}, we can see that the performance of {\tool} is as good as that of the most competitive tools such as CVC4 and Z3 on basic string constraints. In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases. On the APLAS and StringFuzz benchmarks that are SAT, {\tool} does not perfomr as well as the best performing tool. We however do not consider this crucial because both of these benchmarks are artificial, either hand-crafted or randomly generated. On the most important benchmarks, those that come from program analysis, {\tool} is comparable to the best performing tool.

>>>>

From Table~\ref{table:base_benchmark}, we can see that the performance of {\tool} is as good as that of the most competitive tools such as CVC4 and Z3 on basic string constraints. In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases. On the StringFuzz benchmarks that are SAT, {\tool} does not perform as well as the best performing tool. We however do not consider this crucial because these benchmarks are just randomly generated for debugging. On the most important benchmarks, those that come from program analysis, {\tool} is comparable to the best performing tool.
